Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-06-10 report/report.tex
References in alphabetical order
Add more noteable OSM quality studies

The next notable study to assess the quality of OSM data was published by \textbf{(Kunze, 2012)}.
The study applied different methods to assess the completeness of OSM data in two federal states in Germany, mainly by analysing the area difference between the OSM dataset and an administrative dataset.
Finally, a notable study in 2013-2014, conducted by researchers from various universities in Norway and Germany (\textbf{(Fan et al, 2014)}), examined the quality and accuracy in building footprint data of the Munich area, at a time and place where the completeness of the OSM dataset was significantly higher (the results of their study showed that the OSM had captured close to 100\% of all building footprints).
At the time Munich was one of the most developed cities in OSM.
Their study included an insight in the geometrical calculations neccessary to match features and points between two datasets, and how to reliably calculate the metrics needed for the most important and assessible of van Oorts criteria.
Their study revealed that although the feature completeness of OSM was high, some architectural details were missing.
The results reveal that the positional accuracy of OSM data at the time was about 4 meters.

@@

@@

@@

>>>>

The next notable study to assess the quality of OSM data was published by \textbf{(Kunze, 2012)}.
The study applied different methods to assess the completeness of OSM data in two federal states in Germany, mainly by analysing the area difference between the OSM dataset and an administrative dataset.

Other notable studies about OSM data accuracy were made around the same time by in Germany by \textbf{Zielstra and Zipf, 2010} and \textbf{Neis et al, 2012}, as well as in France by \textbf{Girres and Touya, 2010}.

Finally, a notable study in 2013-2014, conducted by researchers from various universities in Norway and Germany (\textbf{(Fan et al, 2014)}), examined the quality and accuracy in building footprint data of the Munich area, at a time and place where the completeness of the OSM dataset was significantly higher (the results of their study showed that the OSM had captured close to 100\% of all building footprints).
At the time Munich was one of the most developed cities in OSM.
Their study included an insight in the geometrical calculations neccessary to match features and points between two datasets, and how to reliably calculate the metrics needed for the most important and assessible of van Oorts criteria.
Their study revealed that although the feature completeness of OSM was high, some architectural details were missing.
The results reveal that the positional accuracy of OSM data at the time was about 4 meters.

@@

\bibitem{girres-10}
Girres, J.F. and Touya, G. (2010). Quality assessment of the French OpenStreetMap dataset. Trans. GIS 2010, 14, 435–459.

@@

\bibitem{neis-12}
Neis, P., Zielstra, D. and Zipf, A. (2012). The Street Network Evolution of Crowdsourced Maps: OpenStreetMap in Germany 2007–2011. Future Internet. 2012; 4(1):1-21.

@@

\bibitem{zielstra-10}
Zielstra, D. and Zipf, A. (2010). A Comparative Study of Proprietary Geodata and Volunteered Geographic Information for Germany. In Proceedings of 13th AGILE International Conference on Geographic Information Science, Guimarães, Portugal, 10–14 May 2010.
